---
title: "README"
author: Di Chen
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### msudatapull package Documents

msudatapull is an R package with a collection of functions that perform the data querying and processing on the flyer. The functions are designed to allow users to pass a list of pids or a dataframe to get back the values of the derived fields such as finanical aid, first gen, etc.


#### 1.Installation from MSUgitlab

```{r, results='hide', eval=FALSE}
devtools::install_git(
  "https://chendi4@gitlab.msu.edu/chendi4/msudatapull.git", 
  credentials = git2r::cred_user_pass("chendi4", "your git lab password")
)
```

Note: to successfully install the package:

+ check the installation and load of devtool package

```{r, results='hide', eval=FALSE}
if(! 'devtools ' %in% installed.packages()){install.packages('devtools')}
```

+ check your JAVA home and R version, 64 bit on both 

```{r, results='hide', eval=FALSE}
Sys.getenv("JAVA_HOME")
Sys.getenv("R_ARCH")
```

+ Step up your JAVA home 

```{r, results='hide', eval=FALSE}
Sys.setenv(JAVA_HOME='C:/Program Files/Java/jre1.8.0_144')
```

+ [check if jvm.dll is in your windows PATH variable ](https://stackoverflow.com/questions/7019912/using-the-rjava-package-on-win7-64-bit-with-r) 


##### Alternatively, clone the repository to your local directory using git and install from your local directory

#### 2.Load Package to the enviroment
```{r, results='hide', eval=FALSE}
library(msudatapull)
```


#### 3.In order to connect to MSUDATA, the msudatacon function always needs to be called first. The connection is done by JDBC installed in following directory
##### The function will call another function to prompt the password window
```{r,, results='hide', eval=FALSE}
drv <- RJDBC::JDBC("com.microsoft.sqlserver.jdbc.SQLServerDriver","S:/Utilities/Microsoft JDBC Driver 4.0 for SQL Server/sqljdbc_4.0/enu/sqljdbc4.jar")
msudatacon(userid = "chendi4")
```

#### 4.Check the function documentation
```{r, results='hide', eval=FALSE}
?msudatacon
```

### Functions
+ **msudatacon** set up connection to msudata 
+ **cohort**  find which cohort the population specified is from (extend PAG)
+ **firstgen_pull** admission first gen status for population specified (extend PAG) 
+ **honor_pull** honor SCLR status for population specified (extend PAG)
+ **mjrclass_pull** primary major class code by Pid and term for population specified
+ **FA_pull** FA information by Pid and AidYr for population specified
+ **gndr_race_pull** gender and race/ethnicity pull from SISFull or SISInfo for population specified (extend PAG)
+ **Preliminary.PFS2** provide the 1st Spring and 2nd Fall persistence for undergraduate fall entering cohort including summer starters from SISFrzn extracts
+ **Full.PFS2** provide the 1st Spring and 2nd Fall persistence for undergraduate fall entering cohort including summer starters from SISFull
+ **pregpa_pull** provide MSU calculated GPA (zero recoded as Null) for the population specified
+ **firstATL_pull** provide 1st WRA course and Grade for the population specified. If multiple WRA in same first term, lowest course code is chosen
+ **firsttermgpa_pull** provide first term term GPA for the population specified (if term gpa credit is zero, recode to null) 
+ **indicator_pull** provide indicator values on scale from 1-7 for the population specified (null for level other than AT and UN)
+ **rsadress_pull** provide residence address country, state, county from SISPRSN for the population specified. If SISFrzn used, it uses qtrterm extract to get the status as entry term.
+ **term.enroll** provide unit record data on term enrollment including the official enrollment if specifying SISFrzn