---
title: "README"
author: Di Chen
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### msudatapull package Documents

msudatapull is an R package with a collection of functions that perform the data querying and processing on the flyer. The functions are designed to allow users to pass a list of pids or a dataframe to get back the values of the derived fields such as finanical aid, first gen, etc.


#### 1.Installation
To install this package from github please first install and load the devtools package
```{r, results='hide', eval=FALSE}
devtools::install_github("chendi1020/msudatapull")
```

#### 2.Load Package to the enviroment
```{r, results='hide', eval=FALSE}
library(msudatapull)
```


#### 3.In order to connect to MSUDATA, the msudatacon function always needs to be called first. The connection is done by JDBC installed in following directory

```{r,, results='hide', eval=FALSE}
drv <- RJDBC::JDBC("com.microsoft.sqlserver.jdbc.SQLServerDriver","S:/Utilities/Microsoft JDBC Driver 4.0 for SQL Server/sqljdbc_4.0/enu/sqljdbc4.jar")
msudatacon(userid = "***", password = "***")
```

#### 4.Check the function documentation
```{r, results='hide', eval=FALSE}
?msudatacon
```

### Functions
+ msudatacon
+ cohort
+ firstgen_pull
+ honor_pull
+ mjrclass_pull 
+ FA_pull
+ gndr_race_pull